---
title: "Assignment_7"
author: "Rahul Bagga"
date: "10/19/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Markowitz Mean-Variance Portfolio 
#Efficient Frontier 
## Loading packages
```{r}
library(quadprog)
library(ggplot2)
```
 
Loading the returns for each stock A,B,C with 5%, 4% and 6% returns respectively
```{r}
mu_return_vector <- c(0.05, 0.04, 0.06) 
```
Load the sigma or covariance matrix
```{r}
sigma <- matrix(c(0.01, 0.002, 0.005, 
                  0.002, 0.008, 0.006, 
                  0.005, 0.006, 0.012), 
                nrow=3, ncol=3)
```
Loading all the constrains for the quadratic equation for Markowitz Mean-Variance Portfolio 
```{r}
D.Matrix <- 2*sigma
d.Vector <- rep(0, 3)
A.Equality <- matrix(c(1,1,1), ncol=1)
A.Matrix <- cbind(A.Equality, mu_return_vector, 
                  diag(3))

```
As it is given that minimum value of the return is 3.5% and the maximum value is 6%.
```{r}
return_val <- seq(0.035, 0.06, 0.001)
risk_val <- rep(0, length(return_val))
``` 

Setting the return values on b-Vector and solving the Quadratic Equation 
```{r}
for (t in 1:length(return_val)) {
  b.Vector <- c(1, return_val[t], rep(0, 3))
  out <- solve.QP(Dmat=D.Matrix, dvec=d.Vector, 
                  Amat=A.Matrix, bvec=b.Vector, 
                  meq=1)
  risk_val[t] <- out$value
}
```

Creating a dataframe for risk values to plot using ggplot
```{r}
df <- data.frame(return_val, risk_val)
```

Plotting the efficient frontier graph to show the Returns with respect to Risk Tolerance

```{r}
g <- ggplot(df, aes(risk_val, return_val)) + geom_line()
g+ggtitle("Efficient Frontier")+xlab("Risk Appetite")+ylab("Expected Return")
```


